Computational tools for representation theory of affine Lie algebras

### 2009-07-09 AffineLieAlgebras/ACMS2009/notes.tex
Some work on WZW-models

\subsection{Модели Весса-Зумино-Новикова-Виттена}
\label{sec:WZNW}
Модели Весса-Зумино-Новикова-Виттена - это простейшие не минимальные модели двумерной конформной теории поля. Алгебра симметрии в них представляют собой полу прямое произведение алгебры Вирасоро и аффинной алгебры Ли.

>>>>

\subsection{Wess-Zumino-Novikov-Witten models}
\label{sec:WZNW}

Let's start with non-linear $\sigma$-model.
\begin{equation}
  \label{eq:48}
  S_0=\frac{1}{4a^2}\int d^2x\; Tr' (\partial^{\mu}g^{-1}\partial_{\mu}g)
\end{equation}
Here $a^2>0$ is a positive parameter, $g(x)\in G$ - field on Lie group $G$, which we will assume to be semi-simple and by $Tr'$ we have denoted representation independent trace of Lie algebra $\mathfrak{g} $
\begin{equation}
  \label{eq:70}
  Tr'=\frac{1}{x_{rep}}Tr
\end{equation}
$x_{rep}$ is the Dynkin index of the representation.

In this model the conformal invariance is lost at the quantum level, as it can be seen along the lines of previous sections.
!!! Show it by example !!!

Also we can see that holomorphic and antiholomorphic currents aren't conserved individually. The equations of motion are
\begin{equation}
  \label{eq:71}
  \partial^{\mu}(g^{-1}\partial_{\mu}g)=0
\end{equation}
The currents are
\begin{equation}
  \label{eq:currents}
  J_{\mu}=g^{-1}\partial_{\mu}g
\end{equation}
or in the complex coordinates
\begin{equation}
  \label{eq:74}
  \begin{matrix}
    & \tilde{J}_z=g^{-1}\partial_z g, & \tilde{J}_{\bar{z}}=g^{-1}\partial_{\bar{z}}g\\
    & \partial_z \tilde{J}_{\bar{z}}+\partial_{\bar{z}}\tilde{J}_z=0 & \\
  \end{matrix}
\end{equation}
The terms of the equation of motion can not be null separately because $\partial_{\mu}(\epsilon^{\mu\nu}J_{\nu})\neq 0$.

So we add WZ-term to the action and redefine the currents in more appropriate way
\begin{equation}
  \label{eq:72}
  J_z=\partial_z g\;g^{-1}, \qquad J_{\bar{z}}=g^{-1}\partial{\bar z}g
\end{equation}

Модели Весса-Зумино-Новикова-Виттена - это простейшие не минимальные модели двумерной конформной теории поля. Алгебра симметрии в них представляют собой полу прямое произведение алгебры Вирасоро и аффинной алгебры Ли.
